SPA: An Apache Spark Pilot scheduler for HPC applications

### 2019-02-24 paper.tex
added abstract

\begin{abstract}
    \todo{complete}
\end{abstract}

>>>>

\begin{abstract}
    With the recent influx of neuroimaging Big Data, many researchers are moving
    towards adopting Big Data processing engines such as Apache Spark 
    to process the data. These processing engines, however, have been primarily 
    designed to work on dedicated infrastructure and are not well designed to 
    work on infrastructure typically available to researchers, such as 
    High-Performance Computing (HPC) infrastructure. Typical mechanisms for 
    launching Spark-based applications on HPC clusters involve batch-requesting
    of the resources which can greatly increase queueing times of the Big Data 
    applications. Pilot-scheduling techniques is a well known HPC scheduling
    strategy that begins scheduling as compute resources are allocated to the 
    user, thereby reducing HPC scheduling wait times. Here, we introduce SPA, an
    open-source
    pilot-job submission system designed for launching Apache Spark pipelines 
    on Slurm-based clusters. SPA leverages optimizations available in Spark, 
    such as robust workers, masters and driver, in addition to checkpointing, 
    to ensure that processing occurs even when nodes are lost due to timeout. 
    SPA also ensures that a user-specified number of pilots (nodes) have been 
    requested on the cluster in order to ensure a constant level of parallelism.
    Should pilots be idle for a certain amount of time, they are terminated by 
    the system.

\end{abstract}
